Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-06 Tex/Old text/chapters/chapter02.tex
added recent version of ESBMC
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C~\cite{esbmc2018}, C++~\cite{RamalhoFSMC013}, Qt~\cite{MonteiroGCF17}, and CUDA~\cite{PereiraASMMFC17} programs, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.

>>>>

The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C~\cite{esbmc2018,GadelhaMCN19}, C++~\cite{RamalhoFSMC013}, Qt~\cite{MonteiroGCF17}, and CUDA~\cite{PereiraASMMFC17} programs, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}.
